MetaTracts - A Method for Robust Extraction and Visualization of Carbon Fiber Bundles in Fiber Reinforced Composites

### 2014-12-11 metaTracts-pvis2014.tex
minor changes
spell check pass

\newcommand{\replacedWith}[2]{\replaced{#1} \added{#2}}

@@

%% Abstract section.
\abstract{
This work introduces MetaTracts, a novel method  for extracting and visualizing individual fiber bundles and weaving patterns from X-ray computed tomography (XCT) scans of endless carbon fiber reinforced  polymers (CFRP). The proposed work flow is designed to analyze unit cells of CFRP materials integrating the recurring weaving pattern. It is designed to handle XCT scans of low resolution, in which individual fibers are not visible or are barely visible. 
First, a coarse version of integral curves is used to trace subsections of the individual fiber bundles in the woven CFRP materials. We call these sections MetaTracts.
In the second step, these extracted fiber bundle sections (MetaTracts) are clustered using a two step approach: first by orientation, then by proximity.
The tool can generate volumetric representations as well as surface models of the extracted fiber bundles to be exported for further analysis.
We evaluate the proposed work flow on a number of real world datasets and demonstrate that MetaTracts effectively and robustly identifies and separates different fiber bundles. 
%mention user study here?%
%This work will provide a stepping stone to introduce novel non destructive testing techniques for reinforced fiber bundles analysis.
} % end of abstract

>>>>

\newcommand{\replacedWith}[2]{\replaced{#1}\added{#2}}

@@

%% Abstract section.
\abstract{
This work introduces MetaTracts, a novel method  for extracting and visualizing individual fiber bundles and weaving patterns from X-ray computed tomography (XCT) scans of endless carbon fiber reinforced  polymers (CFRP). The proposed work flow is designed to analyze unit cells of CFRP materials integrating the recurring weaving pattern. It is designed to handle XCT scans of low resolution, in which individual fibers are not visible or are barely visible. 
First, a coarse version of integral curves is used to trace subsections of the individual fiber bundles in the woven CFRP materials. We call these sections MetaTracts.
In the second step, these extracted fiber bundle sections (MetaTracts) are clustered using a two-step approach: first by orientation, then by proximity.
The tool can generate volumetric representations as well as surface models of the extracted fiber bundles to be exported for further analysis.
We evaluate the proposed work flow on a number of real world datasets and demonstrate that MetaTracts effectively and robustly identifies and separates different fiber bundles. 
%mention user study here?%
%This work will provide a stepping stone to introduce novel non destructive testing techniques for reinforced fiber bundles analysis.
} % end of abstract
